---
title: "simpleRegress"
author: "John Garza"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  


```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```
## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE(residual standard error) where smaller is better.

The models above provide a representation of the Residual Standard Error.  
The order is formed from the best to worst individual models.  
The smallest Residual Standard Error Value is first because smaller is better.  
This is why the graph for the first model has the most dots that appear the nearest to the abline.  
The best model is the head length model with the Residual Standard Error value that is 4.23.  
The second best model is the chest model with a Residual Standard Error value that is 4.93.  
The third best model is the neck model with a Residual Standard Error value that is 5.37.  
The fourth best model is the weight model with a Residual Standard Error value that is 5.43.  
The fifth best model is the head width model with a Residual Standard Error value that is 7.32.  
The sixth best model is the age model with a Residual Standard Error value that is 7.511.  
